An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-01 EconGrowth2.Rnw
Fixed some wording in the paper.

The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Parameters_No_Energy}.

@@

The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Parameters_With_Q}
and Figure~\ref{fig:CDq_Params_Graph}.

@@

The 95\% confidence intervals associated 
with Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} 
and \ref{fig:CES_sigma_1_delta_1_Scatter_Graph}
are shown in Tables~\ref{tab:CES_Parameters_A} 
and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.

@@

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="none")
@

The 95\% confidence intervals for the ($kl$)$e$ nesting associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.

@@

The 95\% confidence intervals for the ($le$)$k$ nesting associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_lek}--\ref{fig:CESq_sigma_delta_Scatter_Graph_lek}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.

@@

The 95\% confidence intervals for the ($ek$)$l$ nesting associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_ekl}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.

>>>>

The 95\% confidence intervals associated with 
the without-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Parameters_No_Energy}.

@@

The 95\% confidence intervals associated with 
the with-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
are shown in Table~\ref{tab:CD_Parameters_With_Q}
and Figure~\ref{fig:CDq_Params_Graph}.

@@

The 95\% confidence intervals associated 
with ($kl$) nest columns of 
Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
are shown in Tables~\ref{tab:CES_Parameters_A} 
and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.

@@

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy, ($kl$) nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="none")
@

The 95\% confidence intervals associated 
with ($kl$)$e$ nest columns of 
Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.

@@

The 95\% confidence intervals associated 
with ($le$)$k$ nest columns of 
Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.

@@

The 95\% confidence intervals associated 
with ($ek$)$l$ nest columns of 
Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.
